Motivation

### 2017-07-17 Reports/USAID.tex
reportes USAID

---
title: "Motivation"
output: 
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Mexican labour courts face a large and growing backlog of cases. The backlog is made worse by case settlement rates that are low by international standards. Our previous work suggests that one cause of the low settlement rates is that parties are overconfident of their chances of success. We tested this hypothesis through an experimental intervention in the Mexico City Labour Court (MCLC). In a pilot project in the MCLC, we provided objective statistical information to parties in randomly selected cases to see if this information changed the likelihood of parties reach a settlement. An initial 12-week pilot in one of the MCLC’s 20 subcourts showed that providing objective information nearly doubled settlement rates on the same day. Given these initial results, we then increased the scale of the project for a second intervention to confirm the result.

These experiments required that we generate information to share with workers. We produced a set of predictive models using data from cases filed in 2011.We refer to the resulting product as a “calculator.” The predicted outcomes are based on information in case filings, including the wage and tenure of the worker, and other variables described in more detail below. Each of the MCLC’s 20 subcourts handles cases originating from disputes in a given set of industries. Thus, the predictive information needed to be based on information from the relevant subcourts.

@@

# First Pilot 
## Data
The data for the calculator developed for the pilot came from a sample of 1000 concluded case files from a single subcourt (subcourt 7). Defendants in subcourt 7 consist mostly of firms in XXX industries, so we were careful in correctly labeling casefiles containing at least one outsourcing firm within the list of defendants.

We coded data directly from casefiles, and then randomly inspected 20% of the data entries by comparing the manually coded databases against the actual casefiles to ensure that the initial coding was accurate. Our data cleaning process was fairly standard. We then examined the data for outliers, recoding as necessary We excluded a small number of cases for which key information was missing.

## Models
### Our questions

@@

1. How likely is settlement, abandonment by the plaintiff, expiry, or a judicial decision in favour of either party?

2. Given a particular outcome, what was the expected duration for the entire process?

3. Given a particular outcome, what was the expected compensation at the end of the process?

@@

### Training and Evaluation

@@

#### Probability of outcomes

@@

- Settlement

- Expiry

- Court Ruling with a positive compensation

- Court Ruling with no compensation

- Drop

@@

D. Single-hidden-layer Neural Network (20 nodes in the hidden layer and 10% weight decay)

@@

**XXX (1) **
** Propuestas:** 
**A. Poner unos histogramas de accuracy rate entre modelos **
**B. Poner unas tablitas de la métrica en cuestión (i.e. accuracy rate y MAPD) **

#### Prediction models

@@

The 7 models to be used in the calculator were chosen based on the *MAPD (Mean Absolute Percentage Deviation).* This evaluation measure was chosen because we had no zero values in our dependent variables and were inclined to giving rather conservative predictions to parties.

**XXX (2) **
** Propuestas:** 
**A. Poner unas scatter plots de y vs. ygorro como las que hice para el paper. **
**B. Poner unas tablitas de la métrica en cuestión (i.e. accuracy rate y MAPD)**

## Information

@@

![Calculator predictions in the first pilot](../Paper/Figuras/calctreat.png)

# Scale-Up
## Data

@@

## Models

@@

### Our Questions

@@

1. Given a case ending in a court ruling, how likely is to recover a positive compensation?

2. What would be that expected compensation?

3. Given a case ending in settlement, what would be the expected compensation?

### Training and Evaluation
#### Probability of winning

Our classification problem became slightly different. In order to assess the unbalancedness of our court rulings sample -only 24% of court rulings ever recover something- we used a Synthetic Minority Over-Sampling Technique -see [(Chawla et.al., 2002)](http://jair.org/media/953/live-953-2037-jair.pdf) for more detail- and did a 80-20 train vs. test split on our data.

@@

Our final model resulted in a Random Forest of 1200 CARTs, which yielded an 86% accuracy rate on test classification.

#### Expected compensations

@@

**XXX (3)** 
** Aquí tenemos las grafiquitas de las distribuciones de errores con las que evaluamos los modelos (les anexo el doc, por si no lo recuerdan). Puedo poner esas, aunque no me encantan, puedo poner una tablita con los MSE, puedo hacer otras... Como me digan**

## Information

@@

**XXX Este me falta**

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Motivation},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Motivation}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\begin{document}
\maketitle

Mexican labour courts face a large and growing backlog of cases. The
backlog is made worse by case settlement rates that are low by
international standards. Our previous work suggests that one cause of
the low settlement rates is that parties are overconfident of their
chances of success. We tested this hypothesis through an experimental
intervention in the Mexico City Labour Court (MCLC). In a pilot project
in the MCLC, we provided objective statistical information to parties in
randomly selected cases to see if this information changed the
likelihood of parties reach a settlement. An initial 12-week pilot in
one of the MCLC's 20 subcourts showed that providing objective
information nearly doubled settlement rates on the same day. Given these
initial results, we then increased the scale of the project for a second
intervention to confirm the result.

These experiments required that we generate information to share with
workers. We produced a set of predictive models using data from cases
filed in 2011.We refer to the resulting product as a ``calculator.'' The
predicted outcomes are based on information in case filings, including
the wage and tenure of the worker, and other variables described in more
detail below. Each of the MCLC's 20 subcourts handles cases originating
from disputes in a given set of industries. Thus, the predictive
information needed to be based on information from the relevant
subcourts.

@@

\section{First Pilot}\label{first-pilot}

\subsection{Data}\label{data}

The data for the calculator developed for the pilot came from a sample
of 1000 concluded case files from a single subcourt (subcourt 7).
Defendants in subcourt 7 consist mostly of firms in XXX industries, so
we were careful in correctly labeling casefiles containing at least one
outsourcing firm within the list of defendants.

We coded data directly from casefiles, and then randomly inspected 20\%
of the data entries by comparing the manually coded databases against
the actual casefiles to ensure that the initial coding was accurate. Our
data cleaning process was fairly standard. We then examined the data for
outliers, recoding as necessary We excluded a small number of cases for
which key information was missing.

\subsection{Models}\label{models}

\subsubsection{Our questions}\label{our-questions}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  How likely is settlement, abandonment by the plaintiff, expiry, or a
  judicial decision in favour of either party?
\item
  Given a particular outcome, what was the expected duration for the
  entire process?
\item
  Given a particular outcome, what was the expected compensation at the
  end of the process?
\end{enumerate}

@@

\subsubsection{Training and Evaluation}\label{training-and-evaluation}

@@

\paragraph{Probability of outcomes}\label{probability-of-outcomes}

@@

\begin{itemize}
\item
  Settlement
\item
  Expiry
\item
  Court Ruling with a positive compensation
\item
  Court Ruling with no compensation
\item
  Drop
\end{itemize}

@@

D. Single-hidden-layer Neural Network (20 nodes in the hidden layer and
10\% weight decay)

@@

\textbf{XXX (1) } ** Propuestas:** \textbf{A. Poner unos histogramas de
accuracy rate entre modelos } \textbf{B. Poner unas tablitas de la
métrica en cuestión (i.e.~accuracy rate y MAPD) }

\paragraph{Prediction models}\label{prediction-models}

@@

The 7 models to be used in the calculator were chosen based on the
\emph{MAPD (Mean Absolute Percentage Deviation).} This evaluation
measure was chosen because we had no zero values in our dependent
variables and were inclined to giving rather conservative predictions to
parties.

\textbf{XXX (2) } ** Propuestas:** \textbf{A. Poner unas scatter plots
de y vs.~ygorro como las que hice para el paper. } \textbf{B. Poner unas
tablitas de la métrica en cuestión (i.e.~accuracy rate y MAPD)}

\subsection{Information}\label{information}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../Paper/Figuras/calctreat.png}
\caption{Calculator predictions in the first pilot}
\end{figure}

\section{Scale-Up}\label{scale-up}

\subsection{Data}\label{data-1}

@@

\subsection{Models}\label{models-1}

@@

\subsubsection{Our Questions}\label{our-questions-1}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Given a case ending in a court ruling, how likely is to recover a
  positive compensation?
\item
  What would be that expected compensation?
\item
  Given a case ending in settlement, what would be the expected
  compensation?
\end{enumerate}

\subsubsection{Training and Evaluation}\label{training-and-evaluation-1}

\paragraph{Probability of winning}\label{probability-of-winning}

Our classification problem became slightly different. In order to assess
the unbalancedness of our court rulings sample -only 24\% of court
rulings ever recover something- we used a Synthetic Minority
Over-Sampling Technique -see
\href{http://jair.org/media/953/live-953-2037-jair.pdf}{(Chawla et.al.,
2002)} for more detail- and did a 80-20 train vs.~test split on our
data.

@@

Our final model resulted in a Random Forest of 1200 CARTs, which yielded
an 86\% accuracy rate on test classification.

\paragraph{Expected compensations}\label{expected-compensations}

@@

\textbf{XXX (3)} ** Aquí tenemos las grafiquitas de las distribuciones
de errores con las que evaluamos los modelos (les anexo el doc, por si
no lo recuerdan). Puedo poner esas, aunque no me encantan, puedo poner
una tablita con los MSE, puedo hacer otras\ldots{} Como me digan**

\subsection{Information}\label{information-1}

@@

\textbf{XXX Este me falta}

\end{document}
